%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior fullstack web developer} % Job title
    {Keynua {\normalfont - E-signatures with identity verification for Latin America}} % Organization
    {} % Location
    {June 2020 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of new features with Typescript and Node.js using DynamoDB, SNS, SQS, Lambda functions, and Cloudformation from AWS.}
        \item {Development of user interfaces using Gatsby and React.}
        \item {Development and deployment of a web application for editing PDF files using PSPDFKit and AWS ECS.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior web developer} % Job title
    {Qempo {\normalfont - US products ecommerce in Peru}} % Organization
    {} % Location
    {March 2018 - May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development and deployment of the second and third versions of the Qempo backend services, using PostgreSQL, Flask and SQLAlchemy.}
        \item {Development of message queuing software for sending emails and other asynchronous tasks, using RabbitMQ and Celery.}
        \item {Integrated Qempo backend services with Segment, a CDP.}
        \item {Development of a complete web scraping software solution, including desktop applications and backend functionalities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web developer} % Job title
    {ITLAB {\normalfont - IT Laboratory of the Universidad de Lima}} % Organization
    {} % Location
    {July 2016 - June 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of new features for the web application of the cultural center of the Universidad de Lima, with more than 10,000 tickets sold.}
        \item {Implemented and deployed the web application for the international meeting, Relme 31, using HTML, JS, CSS and PHP.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software developer} % Job title
    {AGO {\normalfont - Technology consultant on supply chain management}} % Organization
    {} % Location
    {March 2016 - June 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Application development, for Laive, using C \# and Lingo, with the purpose of optimizing their product production.}
        \item {Developed a similar application, for Primax, used to optimize the production of different fuels.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
